---
title: "PCORnet Query Fulfillment - Alternative Query Language Pilot"
subtitle: "Query 3 - Study-Specific Data Quality Modules"
author: PCORnet Query Fulfillment Center
title-block-banner: "#D5D5D5"
title-block-style: default
title-block-banner-color: "black"
format:
  html: 
    theme: journal
    embed-resources: true
    smooth-scroll: true
    toc: true
    toc-location: left
    toc-depth: 5
    code-copy: true
    code-overflow: wrap
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, 
  output_file = paste0('aql-query-3-final-report-', format(Sys.time(), '%Y%m%d'), '.html') )})
---

```{r setup, include=FALSE}
# Default taken from R notebook behavior: when knitting, wd will always be location of notebook
base_dir <- '..'
Sys.setenv(PEDSNET_SKIP_REQUEST_EXECUTION=1)
tryCatch(source('../site/run.R'),
         error = function (e) message(e)) # May not be able to make db connection

# Set to "local" to read data from ../results, or another value to read from db
data_source <- if_else(config('execution_mode') == 'distribution', 'local', 'not_local')

require(tidyr)
require(knitr)
require(kableExtra)
require(stringr)
require(tibble)
require(ggplot2)
require(ggiraph)
require(plotly)
require(gt)
require(countmaskr)

get_results <- function(tbl_name) {
  if (data_source == 'local') {
    rslt <- read_csv(paste0('../results/', tbl_name, '.csv'))
  }
  else {
    rslt <- results_tbl(tbl_name) %>% collect()
  }
rslt
}

prettify_kable <- function(data) {
  data %>% kable(digits = 4, format.args = list(big.mark = ',')) %>%
    kable_styling(bootstrap_options = c("striped", "hover")) %>%
    column_spec(1, bold = T, border_right = T)
}

opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

```

# Run Time Breakdown
```{r runtime}

runtime_per_site <- read_csv(paste0(base_dir, '/aql3-data/processed_files/runtime_site.csv')) %>% 
  select(qry_site, site_runtime) %>% 
  mutate(site_runtime = round(site_runtime, 3),
         rt_hours = round(site_runtime / 60, 3))

runtime_per_site %>%
  gt::gt(rowname_col = 'qry_site') %>%
  cols_label('site_runtime' = 'Site Runtime (Minutes)',
             'rt_hours' = 'Site Runtime (Hours)') %>%
  opt_stylize(style = 6, color = 'red') %>%
  grand_summary_rows(columns = c('site_runtime', 'rt_hours'),
                     fns = list('Average' ~ mean(.),
                                'Median' ~ median(.))) %>%
  tab_header('Query Runtime Summary')


```

# Table 1 Summary
```{r tbl1_summ, fig.width=10}

t1_cat_merge <- read_csv(paste0(base_dir, '/aql3-data/processed_files/table1.csv')) %>%
  # group_by(category, value) %>%
  # mutate(site = row_number()) %>%
  group_by(site, label, category) %>%
  summarise(ct = sum(ct)) %>% 
  group_by(site, category) %>%
  mutate(total_site_pt = sum(ct),
         site_prop = ct / total_site_pt,
         site_prop = ifelse(category == 'average_fu', NA, site_prop)) %>%
  ungroup()

t1_total_merge <- t1_cat_merge %>%
  filter(category != 'average_fu') %>%
  group_by(category, label) %>%
  summarise(allsite_ct = sum(ct),
            allsite_mean = mean(site_prop),
            allsite_median = median(site_prop),
            allsite_range = max(site_prop) - min(site_prop),
            allsite_iqr = IQR(site_prop)) %>%
  group_by(category) %>%
  mutate(total_pt = sum(allsite_ct))

# t1_masked <- mask_table(t1_merge %>% filter(category != 'average_fu'),
#                         col_groups = list("ct"),
#                         group_by = c('site', 'category'),
#                         percentages = TRUE,
#                         overwrite_columns = FALSE)

# t1_fu <- t1_merge %>%
#   filter(category == 'average_fu') %>%
#   rename('ct_masked' = ct) %>%
#   mutate(ct_masked = round(ct_masked, 3),
#          ct_masked = as.character(ct_masked))

t1_pivot <- t1_total_merge %>%
  select(label, category, allsite_mean, allsite_median, allsite_range, allsite_iqr) %>%
  ungroup() %>%
  # pivot_wider(names_from = site,
  #             values_from = ct_masked) %>%
  mutate(category = case_when(category == 'age_group' ~ 'Age Group',
                              category == 'race' ~ 'Race',
                              category == 'ethnicity' ~ 'Ethnicity',
                              category == 'average_fu' ~ 'Average Follow-Up',
                              category == 'sex' ~ 'Sex'))

t1_pivot %>%
  arrange(category, label) %>%
  gt::gt(groupname_col = 'category',
         rowname_col = 'label') %>%
  fmt_percent() %>%
  cols_label('allsite_mean' = 'Mean',
             'allsite_median' = 'Median',
             'allsite_range' = 'Range',
             'allsite_iqr' = 'IQR') %>%
  sub_missing(missing_text = '') %>%
  tab_header(title = 'Demographic Table 1 Summary',
             subtitle = 'Based on Percentage of Patients') %>%
  opt_stylize(style = 6, color = 'red')


read_csv(paste0(base_dir, '/aql3-data/processed_files/table1.csv')) %>%
  filter(category == 'average_fu') %>%
  ggplot(aes(y = site, x = ct, fill = site)) +
  geom_col(show.legend = FALSE) +
  theme_minimal() +
  scale_fill_ssdqa() +
  labs(y = 'Data Mart',
       x = 'Average Years of F/U',
       title = 'Average Years of Follow-Up Between First and Last Visit')


```

# Data Quality Analyses

## Module: Cohort Attrition

### Multi Site, Exploratory, No Time

::: panel-tabset

# Step 0
```{r ca_ss_exp_nt0}

## Need to decide how to visualize the single site output

## CONFIGS - log_scale, var_col, what step to start at

s0_ss <- ca_output(process_output = 
                     read_csv(paste0(base_dir, '/aql3-data/processed_files/ca_ms_exp_nt_step0.csv')),
          output_function = 'ca_ms_exp_nt',
          log_scale = FALSE,
          var_col = 'prop_retained_start')

s0_ss[[1]]
```

# Step 3

```{r ca_ss_exp_nt3}
s3_ss <- ca_output(process_output = 
                     read_csv(paste0(base_dir, '/aql3-data/processed_files/ca_ms_exp_nt_step3.csv')),
          output_function = 'ca_ms_exp_nt',
          log_scale = FALSE,
          var_col = 'prop_retained_start')

s3_ss[[1]]

```

# Attrition Metadata
```{r ca_ss_exp_met}

s0_ss[[2]]

```
:::

### Multi Site, Anomaly Detection, No Time

::: panel-tabset

# Step 0
```{r ca_ms_anom_nt0}

## CONFIGS - var_col, what step to start at

s0_ms <- ca_output(process_output = 
                     read_csv(paste0(base_dir, '/aql3-data/processed_files/ca_ms_anom_nt_step0.csv')),
          output_function = 'ca_ms_anom_nt',
          log_scale = FALSE,
          var_col = 'prop_retained_prior')

s0_ms

```

# Step 3

```{r ca_ms_anom_nt3}
s3_ms <- ca_output(process_output = 
                     read_csv(paste0(base_dir, '/aql3-data/processed_files/ca_ms_anom_nt_step3.csv')),
          output_function = 'ca_ms_anom_nt',
          log_scale = FALSE,
          var_col = 'prop_retained_prior')

s3_ms

```

# Attrition Metadata
```{r ca_ms_anom_met}

s0_ss[[2]]

```
:::

## Module: Clinical Events and Specialties

### Single Site, Anomaly Detection, No Time
```{r cnc_sp_ss_anom_nt}

# output_ss_an <- conc_output_gen(conc_process_output= 'read cnc file' ,
#                                 conc_process_names= 'read spc names file',
#                                 multi_or_single_site='single',
#                                 anomaly_or_exploratory='anomaly',
#                                 time_dimension=FALSE,
#                                 facet_vars=c('codeset_name'),
#                                 n_mad=3)
# output_ss_an

```

### Multi Site, Exploratory, No Time
```{r cnc_sp_ms_exp_nt}

# output_ms_exp_nt <- conc_output_gen(conc_process_output= 'read cnc file',
#                                     conc_process_names= 'read spc names file',
#                                     multi_or_single_site='multi',
#                                     anomaly_or_exploratory='exploratory',
#                                     time_dimension=FALSE,
#                                     facet_vars=c('codeset_name'))
# output_ms_exp_nt

```

## Module: Clinical Facts per Patient

### Single Site, Exploratory, Across Time

::: panel-tabset

# C8WCM - Non-Pediatric

```{r pf_ss_exp_at_adult}

adult1 <- pf_output(process_output = read_csv(paste0(base_dir, '/aql3-data/processed_files/pf_ss_at.csv')) %>%
            filter(site == 'C8WCM'),
          output_function = 'pf_ss_exp_at',
          facet = 'visit_type',
          output = 'median_fact_ct',
          date_breaks_str = '1 year')

adult1
```

# C4UMO - Non-Pediatric

```{r pf_ss_exp_at_adult2}

adult2 <- pf_output(process_output = read_csv(paste0(base_dir, '/aql3-data/processed_files/pf_ss_at.csv')) %>%
            filter(site == 'C4UMO'),
          output_function = 'pf_ss_exp_at',
          facet = 'visit_type',
          output = 'median_fact_ct',
          date_breaks_str = '1 year')

adult2 

```

# C7LC - Pediatric

```{r pf_ss_exp_at_peds}

peds <- pf_output(process_output = read_csv(paste0(base_dir, '/aql3-data/processed_files/pf_ss_at.csv')) %>%
            filter(site == 'C7LC'),
          output_function = 'pf_ss_exp_at',
          facet = 'visit_type',
          output = 'median_fact_ct',
          date_breaks_str = '1 year')

peds

```
:::

### Single Site, Anomaly Detection, Across Time

::: panel-tabset

# C8WCM - Non-Pediatric

```{r pf_ss_anom_at_adult}

## CONFIGS - domain & visit filters
## maybe pick two and patchwork?

adult1 <- pf_output(process_output = read_csv(paste0(base_dir, '/aql3-data/processed_files/pf_ss_at.csv')) %>%
            filter(site == 'C8WCM'),
          output_function = 'pf_ss_anom_at',
          facet = NULL,
          visit_filter = 'inpatient',
          domain_filter = 'meds_admin')

adult1

```

# C4UMO - Non-Pediatric

```{r pf_ss_anom_at_adult2}

adult2 <- pf_output(process_output = read_csv(paste0(base_dir, '/aql3-data/processed_files/pf_ss_at.csv')) %>%
            filter(site == 'C4UMO'),
          output_function = 'pf_ss_anom_at',
          facet = NULL,
          visit_filter = 'outpatient',
          domain_filter = 'diagnoses')

adult2

```

# C7LC - Pediatric

```{r pf_ss_anom_at_peds}

peds <- pf_output(process_output = read_csv(paste0(base_dir, '/aql3-data/processed_files/pf_ss_at.csv')) %>%
            filter(site == 'C7LC'),
          output_function = 'pf_ss_anom_at',
          facet = NULL,
          visit_filter = 'inpatient',
          domain_filter = 'procedures')

peds

```
:::

### Single Site, Exploratory, No Time

::: panel-tabset

# C8WCM - Non-Pediatric

```{r pf_ss_exp_nt_adult}

adult1 <- pf_output(process_output = read_csv(paste0(base_dir, '/aql3-data/processed_files/pf_ss_nt.csv')) %>%
            filter(site == 'C8WCM'),
          output_function = 'pf_ss_exp_nt',
          output = 'median_site_without0s',
          facet = 'visit_type')

adult1

```

# C4UMO - Non-Pediatric

```{r pf_ss_exp_nt_adult2}

adult2 <- pf_output(process_output = read_csv(paste0(base_dir, '/aql3-data/processed_files/pf_ss_nt.csv')) %>%
            filter(site == 'C4UMO'),
          output_function = 'pf_ss_exp_nt',
          output = 'median_site_without0s',
          facet = 'visit_type')

adult2

```

# C7LC - Pediatric

```{r pf_ss_exp_nt_peds}

peds <- pf_output(process_output = read_csv(paste0(base_dir, '/aql3-data/processed_files/pf_ss_nt.csv')) %>%
            filter(site == 'C7LC'),
          output_function = 'pf_ss_exp_nt',
          output = 'median_site_without0s',
          facet = 'visit_type')

peds

```
:::

## Module: Expected Variables Present

### Multi Site, Exploratory, No Time
```{r evp_ms_exp_nt, fig.width=10}

evp_output(process_output = read_csv(paste0(base_dir, '/aql3-data/processed_files/evp_ms_exp_nt.csv')),
           output_function = 'evp_ms_exp_nt',
           output_level = 'patient')

```

### Multi Site, Anomaly Detection, Across Time

::: panel-tabset

# Hba1c greater than 8

```{r evp_ms_anom_at1}

## hba1c, ckd, elev bp, keto, anti dib, stroke

evp_eucl <- evp_output(process_output = 
                         read_csv(paste0(base_dir, '/aql3-data/processed_files/evp_ms_anom_at.csv')),
           output_function = 'evp_ms_anom_at',
           output_level = 'patient',
           filter_variable = 'Hba1c greater than 8')

sub <- subplot(evp_eucl[[1]], evp_eucl[[2]]) %>% 
   layout(title = 'Smoothed & Linear Proportion of \n Hba1c greater than 8 Over Time') %>% style(showlegend = FALSE, traces = 1:17)

sub
#evp_eucl[[1]]
#evp_eucl[[2]]
evp_eucl[[3]]

```

# CKD

```{r evp_ms_anom_at2}

evp_eucl <- evp_output(process_output = 
                         read_csv(paste0(base_dir, '/aql3-data/processed_files/evp_ms_anom_at.csv')),
           output_function = 'evp_ms_anom_at',
           output_level = 'patient',
           filter_variable = 'CKD')

sub <- subplot(evp_eucl[[1]], evp_eucl[[2]]) %>% 
   layout(title = 'Smoothed & Linear Proportion of \nCKD') %>% style(showlegend = FALSE, traces = 1:17)

sub
#evp_eucl[[1]]
#evp_eucl[[2]]
evp_eucl[[3]]

```

# Elevated Blood Pressure

```{r evp_ms_anom_at3}

evp_eucl <- evp_output(process_output = 
                         read_csv(paste0(base_dir, '/aql3-data/processed_files/evp_ms_anom_at.csv')),
           output_function = 'evp_ms_anom_at',
           output_level = 'patient',
           filter_variable = 'Elevated Blood Pressure')

sub <- subplot(evp_eucl[[1]], evp_eucl[[2]]) %>% 
   layout(title = 'Smoothed & Linear Proportion of \nElevated Blood Pressure') %>% style(showlegend = FALSE, traces = 1:17)

sub
#evp_eucl[[1]]
#evp_eucl[[2]]
evp_eucl[[3]]

```

# Ketoacidosis

```{r evp_ms_anom_at4}

evp_eucl <- evp_output(process_output = 
                         read_csv(paste0(base_dir, '/aql3-data/processed_files/evp_ms_anom_at.csv')),
           output_function = 'evp_ms_anom_at',
           output_level = 'patient',
           filter_variable = 'Ketoacidosis')

sub <- subplot(evp_eucl[[1]], evp_eucl[[2]]) %>% 
   layout(title = 'Smoothed & Linear Proportion of \nKetoacidosis') %>% style(showlegend = FALSE, traces = 1:17)

sub
#evp_eucl[[1]]
#evp_eucl[[2]]
evp_eucl[[3]]

```

# Second-Line Anti-Diabetic Drugs

```{r evp_ms_anom_at5}

evp_eucl <- evp_output(process_output = 
                         read_csv(paste0(base_dir, '/aql3-data/processed_files/evp_ms_anom_at.csv')),
           output_function = 'evp_ms_anom_at',
           output_level = 'patient',
           filter_variable = 'Second-Line Anti Diabetics')

sub <- subplot(evp_eucl[[1]], evp_eucl[[2]]) %>% 
   layout(title = 'Smoothed & Linear Proportion of \nSecond-Line Anti Diabetic Drugs') %>% style(showlegend = FALSE, traces = 1:17)

sub
#evp_eucl[[1]]
#evp_eucl[[2]]
evp_eucl[[3]]

```

# Stroke

```{r evp_ms_anom_at6}

evp_eucl <- evp_output(process_output = 
                         read_csv(paste0(base_dir, '/aql3-data/processed_files/evp_ms_anom_at.csv')),
           output_function = 'evp_ms_anom_at',
           output_level = 'patient',
           filter_variable = 'Stroke')

sub <- subplot(evp_eucl[[1]], evp_eucl[[2]]) %>% 
   layout(title = 'Smoothed & Linear Proportion of \nStroke') %>% style(showlegend = FALSE, traces = 1:17)

sub
#evp_eucl[[1]]
#evp_eucl[[2]]
evp_eucl[[3]]

```
:::

### Single Site, Anomaly Detection, Across Time

::: panel-tabset

# C6BAY - Non-Pediatric

```{r evp_ss_anom_at_a1}

evp_output(process_output = read_csv(paste0(base_dir, '/aql3-data/processed_files/evp_ss_anom_at.csv')) %>%
             filter(site == 'C6BAY'),
           output_function = 'evp_ss_anom_at',
           output_level = 'patient',
           filter_variable = c('CKD', 'Stroke', 'Elevated Blood Pressure', 'Hba1c greater than 8', 'Second-Line Anti Diabetics', 'Ketoacidosis'))

```

# C4UN - Non-Pediatric

```{r evp_ss_anom_at_a2}

evp_output(process_output = read_csv(paste0(base_dir, '/aql3-data/processed_files/evp_ss_anom_at.csv')) %>%
             filter(site == 'C4UN'),
           output_function = 'evp_ss_anom_at',
           output_level = 'patient',
           filter_variable = c('CKD', 'Stroke', 'Elevated Blood Pressure', 'Hba1c greater than 8', 'Second-Line Anti Diabetics', 'Ketoacidosis'))

```

# C7NCH - Pediatric

```{r evp_ss_anom_at_P1}

evp_output(process_output = read_csv(paste0(base_dir, '/aql3-data/processed_files/evp_ss_anom_at.csv')) %>%
             filter(site == 'C7NCH'),
           output_function = 'evp_ss_anom_at',
           output_level = 'patient',
           filter_variable = c('CKD', 'Stroke', 'Elevated Blood Pressure', 'Hba1c greater than 8', 'Second-Line Anti Diabetics', 'Ketoacidosis'))

```

# C7CHCO - Pediatric

```{r evp_ss_anom_at_p2}

evp_output(process_output = read_csv(paste0(base_dir, '/aql3-data/processed_files/evp_ss_anom_at.csv')) %>%
             filter(site == 'C7CHCO'),
           output_function = 'evp_ss_anom_at',
           output_level = 'patient',
           filter_variable = c('CKD', 'Stroke', 'Elevated Blood Pressure', 'Hba1c greater than 8', 'Second-Line Anti Diabetics', 'Ketoacidosis'))

```
:::

## Module: Concept Set Distribution

### Single Site, Exploratory, No Time

::: panel-tabset

# C10OC - Non-Pediatric

```{r csd_ss_exp_nt_a1}

csd_exp_nt <- csd_output(process_output = 
                           read_csv(paste0(base_dir, '/aql3-data/processed_files/csd_exp_nt.csv')) %>%
             filter(site == 'C10OC'),
           output_function = 'csd_ss_exp_nt')

csd_exp_nt[[1]]
csd_exp_nt[[2]]

```

# C2WF - Non-Pediatric
```{r csd_ss_exp_nt_a2}

csd_exp_nt <- csd_output(process_output = 
                           read_csv(paste0(base_dir, '/aql3-data/processed_files/csd_exp_nt.csv')) %>%
             filter(site == 'C2WF'),
           output_function = 'csd_ss_exp_nt')

csd_exp_nt[[1]]
csd_exp_nt[[2]]

```

# C4UI - Non-Pediatric

```{r csd_ss_exp_nt_a3}

csd_exp_nt <- csd_output(process_output = 
                           read_csv(paste0(base_dir, '/aql3-data/processed_files/csd_exp_nt.csv')) %>%
             filter(site == 'C4UI'),
           output_function = 'csd_ss_exp_nt')

csd_exp_nt[[1]]
csd_exp_nt[[2]]

```

# C7SEACH - Pediatric

```{r csd_ss_exp_nt_p}

csd_exp_nt <- csd_output(process_output = 
                           read_csv(paste0(base_dir, '/aql3-data/processed_files/csd_exp_nt.csv')) %>%
             filter(site == 'C7SEACH'),
           output_function = 'csd_ss_exp_nt')

csd_exp_nt[[1]]
csd_exp_nt[[2]]

```
:::

### Multi Site, Anomaly Detection, No Time

::: panel-tabset

# Second-Line Anti-Diabetic Drugs

```{r csd_ms_anom_nt1}

csd_output(process_output = read_csv(paste0(base_dir, '/aql3-data/processed_files/csd_ms_anom_nt.csv')),
           output_function = 'csd_ms_anom_nt',
           filtered_var = 'second_line_rx',
           concept_col = 'concept_code')

```

# Stroke
```{r csd_ms_anom_nt2}

csd_output(process_output = read_csv(paste0(base_dir, '/aql3-data/processed_files/csd_ms_anom_nt.csv')),
           output_function = 'csd_ms_anom_nt',
           filtered_var = 'stroke',
           concept_col = 'concept_code')

```

# Elevated Blood Pressure
```{r csd_ms_anom_nt3}

csd_output(process_output = read_csv(paste0(base_dir, '/aql3-data/processed_files/csd_ms_anom_nt.csv')),
           output_function = 'csd_ms_anom_nt',
           filtered_var = 'elevated_bp',
           concept_col = 'concept_code')

```

# Ketoacidosis
```{r csd_ms_anom_nt4}

csd_output(process_output = read_csv(paste0(base_dir, '/aql3-data/processed_files/csd_ms_anom_nt.csv')),
           output_function = 'csd_ms_anom_nt',
           filtered_var = 'ketoacidosis',
           concept_col = 'concept_code')

```

# Type 2 Diabetes Diagnosis
```{r csd_ms_anom_nt5}

csd_output(process_output = read_csv(paste0(base_dir, '/aql3-data/processed_files/csd_ms_anom_nt.csv')),
           output_function = 'csd_ms_anom_nt',
           filtered_var = 't2d',
           concept_col = 'concept_code')

```

# CKD
```{r csd_ms_anom_nt6}

csd_output(process_output = read_csv(paste0(base_dir, '/aql3-data/processed_files/csd_ms_anom_nt.csv')),
           output_function = 'csd_ms_anom_nt',
           filtered_var = 'ckd',
           concept_col = 'concept_code')

```
:::

### Multi Site, Exploratory, Across Time
#### Yearly

::: panel-tabset

# Second-Line Anti-Diabetic Drugs

```{r csd_ms_exp_at_year1}

ms_exp_y <- csd_output(process_output = 
             read_csv(paste0(base_dir,'/aql3-data/processed_files/csd_ms_exp_at_year.csv')),
           output_function = 'csd_ms_exp_at',
           filtered_var = 'second_line_rx',
           filter_concept = c(311041, 861004, 242120),
           concept_col = 'concept_code')

ms_exp_y[[1]]
ms_exp_y[[2]]

```

# Stroke

```{r csd_ms_exp_at_year2}

ms_exp_y <- csd_output(process_output = 
             read_csv(paste0(base_dir,'/aql3-data/processed_files/csd_ms_exp_at_year.csv')),
           output_function = 'csd_ms_exp_at',
           filtered_var = 'stroke',
           filter_concept = c('I63.9'),
           concept_col = 'concept_code')

ms_exp_y[[1]]
ms_exp_y[[2]]

```

# Elevated Blood Pressure

```{r csd_ms_exp_at_year3}

ms_exp_y <- csd_output(process_output = 
             read_csv(paste0(base_dir,'/aql3-data/processed_files/csd_ms_exp_at_year.csv')),
           output_function = 'csd_ms_exp_at',
           filtered_var = 'elevated_bp',
           filter_concept = c('R03.0', '796.2'),
           concept_col = 'concept_code')

ms_exp_y[[1]]
ms_exp_y[[2]]

```

# Ketoacidosis

```{r csd_ms_exp_at_year4}

ms_exp_y <- csd_output(process_output = 
             read_csv(paste0(base_dir,'/aql3-data/processed_files/csd_ms_exp_at_year.csv')),
           output_function = 'csd_ms_exp_at',
           filtered_var = 'ketoacidosis',
           filter_concept = c('E10.10', 'E11.00', '250.13'),
           concept_col = 'concept_code')

ms_exp_y[[1]]
ms_exp_y[[2]]

```

# Type 2 Diabetes Diagnosis

```{r csd_ms_exp_at_year5}

ms_exp_y <- csd_output(process_output = 
             read_csv(paste0(base_dir,'/aql3-data/processed_files/csd_ms_exp_at_year.csv')),
           output_function = 'csd_ms_exp_at',
           filtered_var = 't2d',
           filter_concept = c('E11.9', 'E11.65'),
           concept_col = 'concept_code')

ms_exp_y[[1]]
ms_exp_y[[2]]

```

# CKD

```{r csd_ms_exp_at_year6}

ms_exp_y <- csd_output(process_output = 
             read_csv(paste0(base_dir,'/aql3-data/processed_files/csd_ms_exp_at_year.csv')),
           output_function = 'csd_ms_exp_at',
           filtered_var = 'ckd',
           filter_concept = c('E11.22', 'N18.4', 'D63.1'),
           concept_col = 'concept_code')

ms_exp_y[[1]]
ms_exp_y[[2]]

```
:::

#### Quarterly

::: panel-tabset

# Second-Line Anti-Diabetic Drugs

```{r csd_ms_exp_at_qrtr1}

date_list <- read_csv(paste0(base_dir,'/aql3-data/processed_files/csd_exp_at_qrtr.csv')) %>% distinct(time_start)

ms_exp_q <- csd_output(process_output = 
             read_csv(paste0(base_dir,'/aql3-data/processed_files/csd_exp_at_qrtr.csv')),
           output_function = 'csd_ms_exp_at',
           filtered_var = 'second_line_rx',
           filter_concept = c(311041, 861004, 242120),
           concept_col = 'concept_code')

ms_exp_q[[1]]
ms_exp_q[[2]]

```

# Stroke

```{r csd_ms_exp_at_qrtr2}

ms_exp_q <- csd_output(process_output = 
             read_csv(paste0(base_dir,'/aql3-data/processed_files/csd_exp_at_qrtr.csv')),
           output_function = 'csd_ms_exp_at',
           filtered_var = 'stroke',
           filter_concept = c('I63.9'),
           concept_col = 'concept_code')

ms_exp_q[[1]]
ms_exp_q[[2]]

```

# Elevated Blood Pressure

```{r csd_ms_exp_at_qrtr3}

ms_exp_q <- csd_output(process_output = 
             read_csv(paste0(base_dir,'/aql3-data/processed_files/csd_exp_at_qrtr.csv')),
           output_function = 'csd_ms_exp_at',
           filtered_var = 'elevated_bp',
           filter_concept = c('R03.0', '796.2'),
           concept_col = 'concept_code')

ms_exp_q[[1]]
ms_exp_q[[2]]

```

# Ketoacidosis

```{r csd_ms_exp_at_qrtr4}

ms_exp_q <- csd_output(process_output = 
             read_csv(paste0(base_dir,'/aql3-data/processed_files/csd_exp_at_qrtr.csv')),
           output_function = 'csd_ms_exp_at',
           filtered_var = 'ketoacidosis',
           filter_concept = c('E10.10', 'E11.00', '250.13'),
           concept_col = 'concept_code')

ms_exp_q[[1]]
ms_exp_q[[2]]

```

# Type 2 Diabetes Diagnosis

```{r csd_ms_exp_at_qrtr5}

ms_exp_q <- csd_output(process_output = 
             read_csv(paste0(base_dir,'/aql3-data/processed_files/csd_exp_at_qrtr.csv')),
           output_function = 'csd_ms_exp_at',
           filtered_var = 't2d',
           filter_concept = c('E11.9', 'E11.65'),
           concept_col = 'concept_code')

ms_exp_q[[1]]
ms_exp_q[[2]]

```

# CKD

```{r csd_ms_exp_at_qrtr6}

ms_exp_q <- csd_output(process_output = 
             read_csv(paste0(base_dir,'/aql3-data/processed_files/csd_exp_at_qrtr.csv')),
           output_function = 'csd_ms_exp_at',
           filtered_var = 'ckd',
           filter_concept = c('E11.22', 'N18.4', 'D63.1'),
           concept_col = 'concept_code')

ms_exp_q[[1]]
ms_exp_q[[2]]

```
:::

### Multi Site, Anomaly Detection, Across Time
#### Yearly

::: panel-tabset

# Second-Line Anti-Diabetic Drugs

```{r csd_ms_anom_at_year1}

csd_eucl <- csd_output(process_output = 
             read_csv(paste0(base_dir,'/aql3-data/processed_files/csd_ms_anom_at_year.csv')),
           output_function = 'csd_ms_anom_at',
           filtered_var = 'second_line_rx',
           filter_concept = 311041,
           concept_col = 'concept_code')

sub <- subplot(csd_eucl[[1]], csd_eucl[[2]]) %>% 
   layout(title = 'Smoothed & Linear Proportion of \n311041') %>% style(showlegend = FALSE, traces = 1:17)

sub
#evp_eucl[[1]]
#evp_eucl[[2]]
csd_eucl[[3]]

```

# Stroke
```{r csd_ms_anom_at_year2}

csd_eucl <- csd_output(process_output = 
             read_csv(paste0(base_dir,'/aql3-data/processed_files/csd_ms_anom_at_year.csv')),
           output_function = 'csd_ms_anom_at',
           filtered_var = 'stroke',
           filter_concept = 'I63.9',
           concept_col = 'concept_code')

sub <- subplot(csd_eucl[[1]], csd_eucl[[2]]) %>% 
   layout(title = 'Smoothed & Linear Proportion of \nI63.9') %>% style(showlegend = FALSE, traces = 1:17)

sub
#evp_eucl[[1]]
#evp_eucl[[2]]
csd_eucl[[3]]

```

# Elevated Blood Pressure
```{r csd_ms_anom_at_year3}

csd_eucl <- csd_output(process_output = 
             read_csv(paste0(base_dir,'/aql3-data/processed_files/csd_ms_anom_at_year.csv')),
           output_function = 'csd_ms_anom_at',
           filtered_var = 'elevated_bp',
           filter_concept = 'R03.0',
           concept_col = 'concept_code')

sub <- subplot(csd_eucl[[1]], csd_eucl[[2]]) %>% 
   layout(title = 'Smoothed & Linear Proportion of \nR03.0') %>% style(showlegend = FALSE, traces = 1:17)

sub
#evp_eucl[[1]]
#evp_eucl[[2]]
csd_eucl[[3]]

```

# Ketoacidosis
```{r csd_ms_anom_at_year4}

csd_eucl <- csd_output(process_output = 
             read_csv(paste0(base_dir,'/aql3-data/processed_files/csd_ms_anom_at_year.csv')),
           output_function = 'csd_ms_anom_at',
           filtered_var = 'ketoacidosis',
           filter_concept = 'E10.10',
           concept_col = 'concept_code')

sub <- subplot(csd_eucl[[1]], csd_eucl[[2]]) %>% 
   layout(title = 'Smoothed & Linear Proportion of \nE10.10') %>% style(showlegend = FALSE, traces = 1:17)

sub
#evp_eucl[[1]]
#evp_eucl[[2]]
csd_eucl[[3]]

```

# Type 2 Diabetes Diagnosis
```{r csd_ms_anom_at_year5}

csd_eucl <- csd_output(process_output = 
             read_csv(paste0(base_dir,'/aql3-data/processed_files/csd_ms_anom_at_year.csv')),
           output_function = 'csd_ms_anom_at',
           filtered_var = 't2d',
           filter_concept = 'E11.9',
           concept_col = 'concept_code')

sub <- subplot(csd_eucl[[1]], csd_eucl[[2]]) %>% 
   layout(title = 'Smoothed & Linear Proportion of \nE11.9') %>% style(showlegend = FALSE, traces = 1:17)

sub
#evp_eucl[[1]]
#evp_eucl[[2]]
csd_eucl[[3]]

```

# CKD
```{r csd_ms_anom_at_year6}

csd_eucl <- csd_output(process_output = 
             read_csv(paste0(base_dir,'/aql3-data/processed_files/csd_ms_anom_at_year.csv')),
           output_function = 'csd_ms_anom_at',
           filtered_var = 'ckd',
           filter_concept = 'N18.4',
           concept_col = 'concept_code')

sub <- subplot(csd_eucl[[1]], csd_eucl[[2]]) %>% 
   layout(title = 'Smoothed & Linear Proportion of \nN18.4') %>% style(showlegend = FALSE, traces = 1:17)

sub
#evp_eucl[[1]]
#evp_eucl[[2]]
csd_eucl[[3]]

```
:::

### Single Site, Anomaly Detection, Across Time
#### Quarterly

::: panel-tabset

# C10OC - Non-Pediatric

```{r csd_ms_anom_at_quarter1}

csd_anom <- csd_output(process_output = 
             read_csv(paste0(base_dir, '/aql3-data/processed_files/csd_ss_anom_at_qrtr.csv')) %>%
             filter(site == 'C10OC'),
             #vocab_tbl = NULL,
           output_function = 'csd_ss_anom_at',
           concept_col = 'concept_code',
           filter_concept = 'E11.9')

csd_anom[[1]]
csd_anom[[2]]

```

# C2WF - Non-Pediatric

```{r csd_ms_anom_at_quarter2}

csd_anom <- csd_output(process_output = 
             read_csv(paste0(base_dir, '/aql3-data/processed_files/csd_ss_anom_at_qrtr.csv')) %>%
             filter(site == 'C2WF'),
             #vocab_tbl = NULL,
           output_function = 'csd_ss_anom_at',
           concept_col = 'concept_code',
           filter_concept = 'E11.9')

csd_anom[[1]]
csd_anom[[2]]

```

# C4UI - Non-Pediatric

```{r csd_ms_anom_at_quarter3}

csd_anom <- csd_output(process_output = 
             read_csv(paste0(base_dir, '/aql3-data/processed_files/csd_ss_anom_at_qrtr.csv')) %>%
             filter(site == 'C4UI'),
             #vocab_tbl = NULL,
           output_function = 'csd_ss_anom_at',
           concept_col = 'concept_code',
           filter_concept = 'E11.9')

csd_anom[[1]]
csd_anom[[2]]

```

# C7SEACH - Pediatric

```{r csd_ms_anom_at_quarter4}

csd_anom <- csd_output(process_output = 
             read_csv(paste0(base_dir, '/aql3-data/processed_files/csd_ss_anom_at_qrtr.csv')) %>%
             filter(site == 'C7SEACH'),
             #vocab_tbl = NULL,
           output_function = 'csd_ss_anom_at',
           concept_col = 'concept_code',
           filter_concept = 'E11.9')

csd_anom[[1]]
csd_anom[[2]]

```
:::

## Module: Patient Event Sequencing

### Single Site, Exploratory, No Time

#### Application 1: Type 2 Diabetes & CKD Diagnoses

:::panel-tabset

# C11OSU - Non-Pediatric

```{r pes_ss_exp_nt1_a1}

pes_ss1 <- pes_ss_exp_nt(process_output = 
                read_csv(paste0(base_dir, '/aql3-data/processed_files/pes_exp_nt1.csv')) %>% 
                filter(site == 'C11OSU'))

pes_ss1[[1]]
pes_ss1[[2]]

```

# C2WF - Non-Pediatric

```{r pes_ss_exp_nt1_a2}

pes_ss1 <- pes_ss_exp_nt(process_output = 
                read_csv(paste0(base_dir, '/aql3-data/processed_files/pes_exp_nt1.csv')) %>% 
                filter(site == 'C2WF') %>% mutate(num_days = round(num_days, 0)))

pes_ss1[[1]]
pes_ss1[[2]]

```

# C4UI - Non-Pediatric 
```{r pes_ss_exp_nt1_a3}

pes_ss1 <- pes_ss_exp_nt(process_output = 
                read_csv(paste0(base_dir, '/aql3-data/processed_files/pes_exp_nt1.csv')) %>% 
                filter(site == 'C4UI'))

pes_ss1[[1]]
pes_ss1[[2]]

```

# C7CHOP - Pediatric

```{r pes_ss_exp_nt1_p1}

pes_ss1 <- pes_ss_exp_nt(process_output = 
                read_csv(paste0(base_dir, '/aql3-data/processed_files/pes_exp_nt1.csv')) %>% 
                filter(site == 'C7CHOP'))

pes_ss1[[1]]
pes_ss1[[2]]

```

# C7CCHMC - Pediatric

```{r pes_ss_exp_nt1_p2}

pes_ss1 <- pes_ss_exp_nt(process_output = 
                read_csv(paste0(base_dir, '/aql3-data/processed_files/pes_exp_nt1.csv')) %>% 
                filter(site == 'C7CCHMC'))

pes_ss1[[1]]
pes_ss1[[2]]

```

# C7STAN - Pediatric

```{r pes_ss_exp_nt1_p3}

pes_ss1 <- pes_ss_exp_nt(process_output = 
                read_csv(paste0(base_dir, '/aql3-data/processed_files/pes_exp_nt1.csv')) %>% 
                filter(site == 'C7STAN'))

pes_ss1[[1]]
pes_ss1[[2]]

```
:::

#### Application 2: Hba1c > 5.8% & Anti-Diabetic Drug Prescription

::: panel-tabset

# C10OC - Non-Pediatric

```{r pes_ss_exp_nt2_a1}

pes_ss2 <- pes_ss_exp_nt(process_output = 
                read_csv(paste0(base_dir, '/aql3-data/processed_files/pes_exp_nt2.csv')) %>% 
                filter(site == 'C10OC'))

pes_ss2[[1]]
pes_ss2[[2]]

```

# C4UMO - Non-Pediatric
```{r pes_ss_exp_nt2_a2}

pes_ss2 <- pes_ss_exp_nt(process_output = 
                read_csv(paste0(base_dir, '/aql3-data/processed_files/pes_exp_nt2.csv')) %>% 
                filter(site == 'C4UMO'))

pes_ss2[[1]]
pes_ss2[[2]]

```

# C8WCM - Non-Pediatric
```{r pes_ss_exp_nt2_a3}

pes_ss2 <- pes_ss_exp_nt(process_output = 
                read_csv(paste0(base_dir, '/aql3-data/processed_files/pes_exp_nt2.csv')) %>% 
                filter(site == 'C8WCM'))

pes_ss2[[1]]
pes_ss2[[2]]

```

# C7SEACH - Pediatric

```{r pes_ss_exp_nt2_p1}

pes_ss2 <- pes_ss_exp_nt(process_output = 
                read_csv(paste0(base_dir, '/aql3-data/processed_files/pes_exp_nt2.csv')) %>% 
                filter(site == 'C7SEACH'))

pes_ss2[[1]]
pes_ss2[[2]]

```

# C7CHCO - Pediatric
```{r pes_ss_exp_nt2_p2}

pes_ss2 <- pes_ss_exp_nt(process_output = 
                read_csv(paste0(base_dir, '/aql3-data/processed_files/pes_exp_nt2.csv')) %>% 
                filter(site == 'C7CHCO'))

pes_ss2[[1]]
pes_ss2[[2]]

```

# C7LC - Pediatric

```{r pes_ss_exp_nt2_p3}

pes_ss2 <- pes_ss_exp_nt(process_output = 
                read_csv(paste0(base_dir, '/aql3-data/processed_files/pes_exp_nt2.csv')) %>% 
                filter(site == 'C7LC'))

pes_ss2[[1]]
pes_ss2[[2]]

```
:::

### Multi Site, Exploratory, No Time

#### Application 1: Type 2 Diabetes & CKD Diagnoses
```{r pes_ms_exp_nt1, fig.height=7}

pes_ms1 <- pes_ms_exp_nt(process_output = 
                read_csv(paste0(base_dir, '/aql3-data/processed_files/pes_exp_nt1.csv')))

pes_ms1

```

#### Application 2: Hba1c > 5.8% & Anti-Diabetic Drug Prescription
```{r pes_ms_exp_nt2, fig.height=7}

pes_ms2 <- pes_ms_exp_nt(process_output = 
                read_csv(paste0(base_dir, '/aql3-data/processed_files/pes_exp_nt2.csv')))

pes_ms2

```