---
title: "Concept Set Distribution - Euclidean Distance"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_collapsed: yes
    toc_float: yes
---

```{r setup, include=FALSE}
# Default taken from R notebook behavior: when knitting, wd will always be location of notebook
base_dir <- '..'
Sys.setenv(PEDSNET_SKIP_REQUEST_EXECUTION=1)
tryCatch(source('../site/run.R'),
         error = function (e) message(e)) # May not be able to make db connection

# Set to "local" to read data from ../results, or another value to read from db
data_source <- if_else(config('execution_mode') == 'distribution', 'local', 'not_local')

require(tidyr)
require(knitr)
require(kableExtra)
require(stringr)
require(tibble)
require(ggplot2)
require(qicharts2)

get_results <- function(tbl_name) {
  if (data_source == 'local') {
    rslt <- read_csv(paste0('../results/', tbl_name, '.csv'))
  }
  else {
    rslt <- results_tbl(tbl_name) %>% collect()
  }
rslt
}

prettify_kable <- function(data) {
  data %>% kable(digits = 4, format.args = list(big.mark = ',')) %>%
    kable_styling(bootstrap_options = c("striped", "hover")) %>%
    column_spec(1, bold = T, border_right = T)
}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

```

## Multi Site, Anomaly, Across Time

This check displays the Euclidean distance between two time series: the smoothed (Loess) proportion of a user-selected concept for a given site and the all-site average proportion. 

Two graphs are output:

  * a line graph displaying the smoothed proportion of the concept_id at each site over time, with the Euclidean distance available in the tooltip when hovering over the line
  * a line graph displaying the raw (not smoothed) proportion of the concept_id at each site over time
  * a circular bar graph displaying the Euclidean distance from the all-site mean where the fill represents the average Loess proportion over time

```{r ms_anom_at}

# ms_anom_at <- csd_output(process_output = get_results('csd_ms_anom_at'),
#                          output_function = 'csd_ms_anom_at',
#                          filter_concept = 81893)

ms_anom_at <- csd_ms_anom_at(process_output = get_results('csd_ms_at_eucl'))

ms_anom_at[[1]]

ms_anom_at[[2]]

ms_anom_at[[3]]

```