---
title: "Concept Set Distribution Output Library"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_collapsed: yes
    toc_float: yes
---

```{r setup, include=FALSE}
# Default taken from R notebook behavior: when knitting, wd will always be location of notebook
base_dir <- '..'
Sys.setenv(PEDSNET_SKIP_REQUEST_EXECUTION=1)
tryCatch(source('../site/run.R'),
         error = function (e) message(e)) # May not be able to make db connection

# Set to "local" to read data from ../results, or another value to read from db
data_source <- if_else(config('execution_mode') == 'distribution', 'local', 'not_local')

require(tidyr)
require(knitr)
require(kableExtra)
require(stringr)
require(tibble)
require(ggplot2)
require(qicharts2)

get_results <- function(tbl_name) {
  if (data_source == 'local') {
    rslt <- read_csv(paste0('../results/', tbl_name, '.csv'))
  }
  else {
    rslt <- results_tbl(tbl_name) %>% collect()
  }
rslt
}

prettify_kable <- function(data) {
  data %>% kable(digits = 4, format.args = list(big.mark = ',')) %>%
    kable_styling(bootstrap_options = c("striped", "hover")) %>%
    column_spec(1, bold = T, border_right = T)
}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

```

This report is a library of each distinct output available for the Concept Set Distribution (CSD) check. The output below was computed at the most basic level (i.e. without any additional facets). Certain customizations may be made by the user should they desire them.


## Single Site, Exploratory, No Time

The heatmap summarizes the top user-selected number of codes for a user-selected number of variables. When a vocabulary table is provided, the concept name is displayed in the tooltip while hovering over a given section. The accompanying reference table displays the overall denominator count for each variable.

```{r ss_exp_nt}

ss_exp_nt <- csd_output(process_output = get_results('csd_ss_exp_nt'),
                        output_function = 'csd_ss_exp_nt',
                        vocab_tbl = vocabulary_tbl('concept'),
                        num_codes = 5,
                        num_mappings = 10)

ss_exp_nt[[1]]

ss_exp_nt[[2]]

```

## Multi Site, Exploratory, No Time

For each site in the cohort, this table summarizes the counts/proportions of each concept_id within a given variable to give the user an idea of which concepts contribute to the makeup of their variable.

```{r ms_exp_nt}

ms_exp_nt <- csd_output(process_output = get_results('csd_ms_nt'),
                        output_function = 'csd_ms_exp_nt',
                        vocab_tbl = vocabulary_tbl('concept'),
                        num_codes = 10)

ms_exp_nt

```

## Single Site, Anomaly, No Time

This heatmap displays the Jaccard similarity index between concepts within one user-selected variable. A high similarity index indicates the concepts co-occur (i.e. exist within the same patient's record) frequently.

```{r ss_anom_nt}

ss_anom_nt <- csd_output(process_output = get_results('csd_ss_anom_nt'),
                         output_function = 'csd_ss_anom_nt',
                         vocab_tbl = vocabulary_tbl('concept'),
                         filtered_var = 'general_jia')

ss_anom_nt

```

## Multi Site, Anomaly, No Time

For each site in the cohort & each concept in the variable, this graph summarizes how frequently that concept appears (size of the dot), how far away from the mean proportion that concept falls (color of the dot), and whether the distance from the mean constitutes an anomaly (stars).

```{r ms_anom_nt}

ms_anom_nt <- csd_output(process_output = get_results('csd_ms_nt'),
                        output_function = 'csd_ms_anom_nt',
                        vocab_tbl = vocabulary_tbl('concept'),
                        filtered_var = 'uveitis',
                        text_wrapping_char = 80,
                        comparison_col = 'prop_concept',
                        grouped_vars = c('variable', 'concept_id'))

ms_anom_nt

```

## Single Site, Exploratory, Across Time

This line graph displays the proportion of concepts within each variable and how they behave across a user provided time interval. Additional information can be found in the tooltip when the user hovers over a particular line. If they wish to isolate a given concept_id, the user can double click on the appropriate entry in the legend.

```{r ss_exp_at}

ss_exp_at <- csd_output(process_output = get_results('csd_ss_at'),
                        output_function = 'csd_ss_exp_at',
                        vocab_tbl = vocabulary_tbl('concept'),
                        filtered_var = c('general_jia', 'ibd','uveitis'),
                        output_value = 'prop_concept')

ss_exp_at[[1]]

ss_exp_at[[2]]

```

## Multi Site, Exploratory, Across Time

This line graph displays the proportion of concepts at each site for a selection of variable(s) and how they behave across a user provided time interval. Additional information can be found in the tooltip when the user hovers over a particular line. If they wish to isolate a given concept_id, the user can double click on the appropriate entry in the legend.

```{r ms_exp_at}

ms_exp_at <- csd_output(process_output = get_results('csd_ms_at'),
                        output_function = 'csd_ms_exp_at',
                        vocab_tbl = vocabulary_tbl('concept'),
                        filtered_var = c('ibd'),
                        output_value = 'prop_concept')

ms_exp_at[[1]]
ms_exp_at[[2]]

```

## Single Site, Anomaly, Across Time

This check outputs a control chart that highlights anomalies in the proportion of patients per concept_id in the provided variable. A `P Prime` chart is used to account for the high sample size, which means that the standard deviation is multiplied by a numerical constant. Blue dots along the line indicate non-anomalous values, while orange dots are anomalies.

```{r ss_anom_at}

ss_anom_at <- csd_output(process_output = get_results('csd_ss_at'),
                        output_function = 'csd_ss_anom_at',
                        vocab_tbl = vocabulary_tbl('concept'),
                        num_mappings = 10,
                        filtered_var = 'spondyloarthritis'
                        )

ss_anom_at[[1]]

ss_anom_at[[2]]

```

## Multi Site, Anomaly, Across Time

This check displays the area under the curve (AUC) for ONE concept_id across time, for every site in the cohort. The AUC computation itself takes place in the initial processing function to reduce load on the summarization end. During this computation, the all site mean is used as the "gold standard" against which the site-specific proportion associated with a given concept_id is compared. 

Two graphs are output:

  * a line graph displaying the proportion of that concept_id at each site over time, with the AUC values available in the tooltip when hovering over a given line
  * a bar graph comparing the AUC values for each site against the all site overall AUC value

```{r ms_anom_at}

ms_anom_at <- csd_output(process_output = get_results('csd_ms_anom_at'),
                         output_function = 'csd_ms_anom_at',
                         filter_concept = 81893)

ms_anom_at[[1]]

ms_anom_at[[2]]

```