---
title: "Expected Variables Present Output Library"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_collapsed: yes
    toc_float: yes
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, 
  output_file = paste0('evp_output_lib_', format(Sys.time(), '%Y%m%d'), '.html') )}) 
---

```{r setup, include=FALSE}
# Default taken from R notebook behavior: when knitting, wd will always be location of notebook
base_dir <- '..'
Sys.setenv(PEDSNET_SKIP_REQUEST_EXECUTION=1)
tryCatch(source('../site/run.R'),
         error = function (e) message(e)) # May not be able to make db connection

# Set to "local" to read data from ../results, or another value to read from db
data_source <- if_else(config('execution_mode') == 'distribution', 'local', 'not_local')

require(tidyr)
require(knitr)
require(kableExtra)
require(stringr)
require(tibble)
require(ggplot2)
require(qicharts2)

get_results <- function(tbl_name) {
  if (data_source == 'local') {
    rslt <- read_csv(paste0('../results/', tbl_name, '.csv'))
  }
  else {
    rslt <- results_tbl(tbl_name) %>% collect()
  }
rslt
}

prettify_kable <- function(data) {
  data %>% kable(digits = 4, format.args = list(big.mark = ',')) %>%
    kable_styling(bootstrap_options = c("striped", "hover")) %>%
    column_spec(1, bold = T, border_right = T)
}

facet <- NULL

output_level <- 'patient'

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

```

This report is a library of each distinct output available for the Expected Variables Present (EVP) check. The output below was computed at the most basic level (i.e. without any additional facets). Certain customizations may be made by the user should they desire them.

## Single Site, Exploratory, No Time

This output summarizes the proportion of patients that meet the criteria (have at least one occurrence of a concept_id in the related codeset) for a selection of variables.

```{r ss_exp_nt}

evp_output(process_output = get_results('evp_ss_exp_nt'),
           output_function = 'evp_ss_exp_nt',
           output_level = 'patient',
           facet = facet)

```

## Multi Site, Exploratory, No Time

This heatmap summarizes the proportion of patients at each site that meet the criteria for a given variable & site combination. Here, warmer colors indicate a higher proportion of patients/rows related to that variable.

```{r ms_exp_nt}

evp_output(process_output = get_results('evp_ms_exp_nt'),
           output_function = 'evp_ms_exp_nt',
           output_level = 'patient',
           facet = facet)

```

## Single Site, Anomaly, No Time

This heatmap displays the Jaccard similarity index between concept groups. A high similarity index indicates the concept groups co-occur (i.e. exist within the same patient's record) frequently.

```{r ss_anom_nt}

g <- evp_output(process_output = get_results('evp_ss_anom_nt'),
                output_function = 'evp_ss_anom_nt',
                output_level = 'patient',
                facet = facet)

g

```

## Multi Site, Anomaly, No Time

This is a dot plot representing anomalous proportions of patients (or rows) with a given variable. Anomalies represent sites that are anomalous when compared to others for that variable. The shape of the dot represents whether or not it is an anomaly, the color of the dot represents the raw proportion of patients (or rows) for that variable, and the size of the dot represents the MAD.

```{r ms_anom_nt}

evp_output(process_output = get_results('evp_ms_anom_nt'),
           output_function = 'evp_ms_anom_nt',
           output_level = 'patient')

```

## Single Site, Exploratory, Across Time

This line graph displays the proportion of patients belonging to a given variable across a user provided time span. Hovering over the graph will display the exact proportion at each time point for the variable.

```{r ss_exp_at}

g <- evp_output(process_output = get_results('evp_ss_exp_at_agegrp') %>% filter(age_grp != 'No Group'),
           output_function = 'evp_ss_exp_at',
           output_level = 'patient',
           facet = 'age_grp')

g

```

## Multi Site, Exploratory, Across Time

This line graph displays the proportion of patients belonging to a given variable & site within each site across a user provided time span. Hovering over a line will display the exact proportion for that site, variable, and time point.

```{r ms_exp_at}

g <- evp_output(process_output = get_results('evp_ms_exp_at'),
           output_function = 'evp_ms_exp_at',
           output_level = 'patient',
           filter_variable = c('cancer', 'JIA', 'TNFI'),
           facet = facet)

g
```

## Single Site, Anomaly, Across Time

### By Year 

This check outputs a control chart that highlights anomalies in the proportion of patients per variable. A `P Prime` chart is used to account for the high sample size, which means that the standard deviation is multiplied by a numerical constant. Blue dots along the line indicate non-anomalous values, while orange dots are anomalies.

```{r ss_anom_at}

evp_output(process_output = get_results('evp_ss_anom_at_year'),
           output_function = 'evp_ss_anom_at',
           output_level = 'patient',
           filter_variable = 'JIA',
           facet = facet)

```

### By Month or Smaller

With smaller time increments, seasonality can make it difficult to detect true anomalies in a time series. This output computes anomalies while ignoring seasonality and outputs 2 graphs:

- a time series line graph with anomalies highlighted with a red dot
- a 4-facet time series line graph that demonstrates the decomposition of the anomalies to make it more clear how the anomalies were identified

```{r ss_anom_at_mnth}

plt <- evp_output(process_output = get_results('evp_ss_anom_at_month') %>% ungroup(),
                  output_function = 'evp_ss_anom_at',
                  output_level = 'patient',
                  facet = facet,
                  filter_variable = 'JIA')

plt[[1]]

plt[[2]]

```

## Multi Site, Anomaly, Across Time

This check displays the Euclidean distance between two time series: the smoothed (Loess) proportion of a user-selected variable for a given site and the all-site average proportion. 

Three graphs are output:

  * a line graph displaying the smoothed proportion of the variable at each site over time, with the Euclidean distance available in the tooltip when hovering over the line
  * a line graph displaying the raw (not smoothed) proportion of the variable at each site over time
  * a circular bar graph displaying the Euclidean distance from the all-site mean where the fill represents the average Loess proportion over time

```{r ms_anom_at}

ms_anom_at <- evp_ms_anom_at(process_output = get_results('evp_ms_anom_at'),
                             output_level = 'patient',
                             filter_variable = 'JIA')

ms_anom_at[[1]]
ms_anom_at[[2]]
ms_anom_at[[3]]

```