---
title: "PF Check Output Library"
output:
  html_document:
    code_folding: hide
    df_print: paged
    toc: yes
    toc_collapsed: yes
    toc_float: yes
---

```{r setup, include=FALSE}
# Default taken from R notebook behavior: when knitting, wd will always be location of notebook
base_dir <- '..'
Sys.setenv(PEDSNET_SKIP_REQUEST_EXECUTION=1)
tryCatch(source('../site/run.R'),
         error = function (e) message(e)) # May not be able to make db connection

# Set to "local" to read data from ../results, or another value to read from db
data_source <- if_else(config('execution_mode') == 'distribution', 'local', 'not_local')

require(tidyr)
require(knitr)
require(kableExtra)
require(stringr)
require(tibble)
require(ggplot2)
require(ggiraph)
require(gt)
require(plotly)
require(qicharts2)
require(ggcharts)

get_results <- function(tbl_name) {
  if (data_source == 'local') {
    rslt <- read_csv(paste0('../results/', tbl_name, '.csv'))
  }
  else {
    rslt <- results_tbl(tbl_name) %>% collect()
  }
rslt
}

prettify_kable <- function(data) {
  data %>% kable(digits = 4, format.args = list(big.mark = ',')) %>%
    kable_styling(bootstrap_options = c("striped", "hover")) %>%
    column_spec(1, bold = T, border_right = T)
}



```

## Single Site, Exploratory, No Time

This output summarises the median number of facts per patient. The domain is along the y-axis with the median fact count along the x-axis. The user can control what facets are used -- like here, where visit type is the facet option.

```{r ss_exp_nt, echo=FALSE, message=FALSE, warning=FALSE}

pf_output(process_output = get_results('pf_ss_exp_nt'),
              output_function = 'pf_ss_exp_nt',
              facet = c('visit_type'),
              output = 'median_site_without0s')

```

## Single Site, Anomaly Detection, No Time

This output displays the proportion of patients that fall +/- 2 SD away from the mean number of facts per patient. The domain is along the y-axis with the proportion of patients that were identified as outliers along the x-axis. The user can control what facets are used -- like here, where visit type is the facet option.

```{r ss_anom_nt, echo=FALSE, message=FALSE, warning=FALSE}

pf_output(process_output = get_results('pf_ss_anom_nt'),
              output_function = 'pf_ss_anom_nt',
              facet = c('visit_type'),
              output = 'prop_outlier_site_fact')

```

## Multi Site, Exploratory, No Time

The dot plot below shows the median number of facts per patient for each site. The domain is along the y-axis with the median fact count along the x-axis. Each dot is a site value, while the star icon represents the overall median. The user can control what facets are used -- like here, where visit type is the facet option.

```{r ms_exp_nt, echo=FALSE, message=FALSE, warning=FALSE}

pf_output(process_output = get_results('pf_ms_exp_nt'),
              output_function = 'pf_ms_exp_nt',
              facet = c('visit_type'),
              output = 'median_site_without0s')

```

## Multi Site, Anomaly Detection, No Time

This is a K-means cluster analysis comparing each site in order to identify potential outliers. One k-means cluster graph is output for each of the user provided facets, so here, one graph is output per visit type. Any site that is far away from others or not part of a "main" cluster can be considered an outlier.

The number of clusters used in the analysis is controlled by the user.

```{r ms_anom_nt, echo=FALSE, message=FALSE, warning=FALSE}

pf_output(process_output = get_results('pf_ms_anom_nt'),
              output_function = 'pf_ms_anom_nt',
              facet = c('visit_type'),
              kmeans_clusters = 4,
              output = 'median_site_without0s')

```

## Single Site, Exploratory, Across Time

This line and dot graph shows the median fact count for each domain and how it changes across the user provided time period. Median fact count along the y-axis, and time (in years) along the x-axis with each line representing a domain. Facets are controlled by the user.

```{r ss_exp_at, echo=FALSE, message=FALSE, warning=FALSE}

pf_output(process_output = get_results('pf_ss_exp_at'),
              output_function = 'pf_ss_exp_at',
              facet = c('visit_type'),
              output = 'median_fact_ct')

```

## Single Site, Anomaly Detection, Across Time

### By Year

This check outputs a control chart that highlights anomalies in the proportion of patients with a given fact type in the provided variable. A `P Prime` chart is used to account for the high sample size, which means that the standard deviation is multiplied by a numerical constant. Blue dots along the line indicate non-anomalous values, while orange dots are anomalies.

```{r ss_anom_at, echo=FALSE, message=FALSE, warning=FALSE}

pf_output(process_output = get_results('pf_ss_anom_at_year'),
              output_function = 'pf_ss_anom_at',
              facet = c('visit_type'))

```

### By Month or Smaller

With smaller time increments, seasonality can make it difficult to detect true anomalies in a time series. This output computes anomalies while ignoring seasonality and outputs 2 graphs:

- a time series line graph with anomalies highlighted with a red dot
- a 4-facet time series line graph that demonstrates the decomposition of the anomalies to make it more clear how the anomalies were identified

```{r ss_anom_at_month}

ss_anom_at2 <- pf_output(process_output = get_results('pf_ss_anom_at_month'),
                          output_function = 'pf_ss_anom_at',
                          visit_filter = 'outpatient',
                          domain_filter = 'conditions')

ss_anom_at2[[1]]

ss_anom_at2[[2]]

```

## Multi Site, Exploratory, Across Time

This output displays either the median or total (sum) fact count per patient per time point across time, comparing across sites.

```{r ms_exp_at, echo=FALSE, message=FALSE, warning=FALSE}

pf_output(process_output = get_results('pf_ms_exp_at'),
              output_function = 'pf_ms_exp_at',
              facet = c('visit_type'),
              output = 'median_fact_ct')

```

## Multi Site, Anomaly, Across Time

This check displays the Euclidean distance between two time series: the smoothed (Loess) proportion of patients with a user selected fact and visit type combination for a given site and the all-site average proportion. 

Three graphs are output:

  * a line graph displaying the smoothed proportion of patients at each site over time, with the Euclidean distance available in the tooltip when hovering over the line
  * a line graph displaying the raw (not smoothed) proportion of patients at each site over time
  * a circular bar graph displaying the Euclidean distance from the all-site mean where the fill represents the average Loess proportion over time

```{r ms_anom_at, echo=FALSE, message=FALSE, warning=FALSE}

op <- pf_output(process_output = get_results('pf_ms_anom_at'),
                output_function = 'pf_ms_anom_at',
                domain_filter = 'conditions',
                visit_filter = 'outpatient')

op[[1]]
op[[2]]
op[[3]]

```
