---
title: "SCV Check Output Library"
output:
  html_document:
    code_folding: hide
    df_print: paged
    toc: yes
    toc_collapsed: yes
    toc_float: yes
---

```{r setup, include=FALSE}
# Default taken from R notebook behavior: when knitting, wd will always be location of notebook
base_dir <- '..'
Sys.setenv(PEDSNET_SKIP_REQUEST_EXECUTION=1)
tryCatch(source('../site/run.R'),
         error = function (e) message(e)) # May not be able to make db connection

# Set to "local" to read data from ../results, or another value to read from db
data_source <- if_else(config('execution_mode') == 'distribution', 'local', 'not_local')

require(tidyr)
require(knitr)
require(kableExtra)
require(stringr)
require(tibble)
require(ggplot2)
require(ggiraph)
require(gt)
require(plotly)
require(qicharts2)
require(gdtools)

get_results <- function(tbl_name) {
  if (data_source == 'local') {
    rslt <- read_csv(paste0('../results/', tbl_name, '.csv'))
  }
  else {
    rslt <- results_tbl(tbl_name) %>% collect()
  }
rslt
}

prettify_kable <- function(data) {
  data %>% kable(digits = 4, format.args = list(big.mark = ',')) %>%
    kable_styling(bootstrap_options = c("striped", "hover")) %>%
    column_spec(1, bold = T, border_right = T)
}

```

All output was generated in a CDM -> Source vocabulary direction, using CDM (SNOMED) codes related to JIA and the source (ICD) codes they are mapped from. The color schemes are temporary at the moment and are subject to change :)

## Single Site, Exploratory, No Time

The heatmap summarizes the top user-selected number of SNOMED codes for a user-selected number of source ICD codes (code types will vary with domain & user configuration). When a vocabulary table is provided, the concept name is displayed in the tooltip while hovering over a given section. The accompanying reference table displays the total count for each concept

```{r ss_exp_nt, echo=FALSE, message=FALSE, warning=FALSE}

op <- scv_output(process_output = get_results('scv_ss_exp_nt'),
           output_function = 'scv_ss_exp_nt',
           code_type = 'cdm',
           facet = NULL,
           num_codes = 10,
           num_mappings = 10,
           vocab_tbl = vocabulary_tbl('concept'))

op[[1]]

op[[2]]

```

## Single Site, Anomaly Detection, No Time

This output displays the number of mappings associated with each SNOMED code. The user can select either greater or less than the median number of mappings in order to identify anomalies.

```{r ss_anom_nt, echo=FALSE, message=FALSE, warning=FALSE}

scv_output(process_output = get_results('scv_ss_anom_nt'),
           output_function = 'scv_ss_anom_nt',
           code_type = 'cdm',
           facet = NULL,
           rel_to_median = 'greater',
           vocab_tbl = vocabulary_tbl('concept'))

```

## Multi Site, Exploratory, No Time

For each site in the cohort, this table summarizes the counts/proportions of each concept_id mapping pair to give the user an idea of the distributions of mappings for, in this case, a given concept_id

```{r ms_exp_nt, echo=FALSE, message=FALSE, warning=FALSE}

scv_output(process_output = get_results('scv_ms_exp_nt'),
           output_function = 'scv_ms_exp_nt',
           code_type = 'cdm',
           facet = 'site',
           num_codes = 10,
           vocab_tbl = vocabulary_tbl('concept'))

```

## Multi Site, Anomaly Detection, No Time

This output calculates the number of mappings per concept_id, then displays the number of MAD that concept_id from the all site median number of mappings. The user chooses whether to display a number of mappings greater or less than the median -- greater is shown below. Here, warmer colors indicate outlying concept_ids.

```{r ms_anom_nt, echo=FALSE, message=FALSE, warning=FALSE, fig.height = 8}

scv_output(process_output = get_results('scv_ms_anom_nt'),
           output_function = 'scv_ms_anom_nt',
           code_type = 'cdm',
           facet = 'site',
           rel_to_median = 'greater',
           mad_dev = 2,
           vocab_tbl = vocabulary_tbl('concept'))

```

## Single Site, Exploratory, Across Time

For each concept_id, this graph displays the proportion of each source_concept_id across the user-specified time period. Additional metadata about each source_concept_id and time point can be found in the tooltip on hover. A reference table with total counts for each concept_id is also output. 

```{r ss_exp_at, echo=FALSE, message=FALSE, warning=FALSE}

op <- scv_output(process_output = get_results('scv_ss_exp_at'),
           output_function = 'scv_ss_exp_at',
           code_type = 'cdm',
           facet = NULL,
           vocab_tbl = vocabulary_tbl('concept'))

op[[1]]
op[[2]]

```

## Single Site, Anomaly Detection, Across Time

### By Year

This check outputs a control chart that highlights anomalies in the number of mappings per concept_id. Blue dots along the line indicate non-anomalous values, while orange dots are anomalies.

```{r ss_anom_at, echo=FALSE, message=FALSE, warning=FALSE}

scv_output(process_output = get_results('scv_ss_anom_at_year'),
           output_function = 'scv_ss_anom_at',
           code_type = 'cdm',
           facet = NULL)

```

### By Month or Smaller
With smaller time increments, seasonality can make it difficult to detect true anomalies in a time series. This output computes anomalies while ignoring seasonality and outputs 2 graphs:

- a time series line graph with anomalies highlighted with a red dot
- a 4-facet time series line graph that demonstrates the decomposition of the anomalies to make it more clear how the anomalies were identified

```{r ss_anom_at_mnth, echo=FALSE, message=FALSE, warning=FALSE}

op <- scv_output(process_output = get_results('scv_ss_anom_at_month'),
           output_function = 'scv_ss_anom_at',
           code_type = 'cdm',
           filter_concept = '4259507',
           facet = NULL)

op[[1]]

op[[2]]


```

## Multi Site, Exploratory, Across Time

For each concept_id & site, this graph displays the proportion of each source_concept_id across the user-specified time period. Additional metadata about each source_concept_id and time point can be found in the tooltip on hover. A reference table with total counts for each concept_id & site is also output. 

```{r ms_exp_at, echo=FALSE, message=FALSE, warning=FALSE}

op <- scv_output(process_output = get_results('scv_ms_exp_at'),
           output_function = 'scv_ms_exp_at',
           code_type = 'cdm',
           facet = 'site',
           vocab_tbl = vocabulary_tbl('concept'))

op[[1]]
op[[2]]

```

## Multi Site, Anomaly Detection, Across Time

This check displays the Euclidean distance between two time series: the smoothed (Loess) proportion of a user-selected concept pair for a given site and the all-site average proportion. 

Three graphs are output:

  * a line graph displaying the smoothed proportion of the concept_id + source_concept_id pair at each site over time, with the Euclidean distance available in the tooltip when hovering over the line
  * a line graph displaying the raw (not smoothed) proportion of the concept_id + source_concept_id pair at each site over time
  * a circular bar graph displaying the Euclidean distance from the all-site mean where the fill represents the average Loess proportion over time

```{r ms_anom_at, echo=FALSE, message=FALSE, warning=FALSE}

op <- scv_output(process_output = get_results('scv_ms_anom_at'),
           output_function = 'scv_ms_anom_at',
           code_type = 'cdm',
           facet = NULL,
           filter_concept = 4132811,
           filter_mapped = 45586853)

op[[1]]
op[[2]]
op[[3]]

```
